Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-06-10 hpmoon-hpca.tex
More changes

\usepackage{moreverb,url}

@@

The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey}. These kind of problems require a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration. Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality. In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models}, and evolved separately. One example of application of this technique was described in \citep{Kimovski15Parallel}. The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes. A high dimensional problem was used to compare these
alternatives. In \citep{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.  Although in both previous works significant speedups were attained, only a low number of nodes were used (8). However, when increasing the number of islands, the division of each section of the chromosome becomes smaller, and the scalability may be affected by obtaining lower quality solutions in the same amount of time.

@@

The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
the compared algorithms and the used methodology (Section \ref{sec:met}) are presented. 
Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.

@@

These metrics have been used extensively, especially in some of the papers presented previously in Section \ref{sec:soa}.

@@

This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands. After a fixed number of generations, one individual is migrated to another random island. At the end of the run, all PFs of all islands are aggregated in a new one to compute the quality measures. This method as been chosen as it do not require synchronization of the global PF every certain number of generations, as other methods described in Section \ref{sec:soa}, and because it can TERMINAAAAAA
%% some justification on why this was chosen - JJ PABLO: Added 
%
%% And some liaison to next subsection - JJ
This method will be compared to different coevolutionary approaches, that are similar to the baseline, with the exception on the decision space to explore in each island.
\subsection{Coevolutionary algorithms compared}
Three different coevolutionary methods have also been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.

@@

\begin{figure*}
\centering
\includegraphics[width=12cm]{islandNoDisjoint.jpg}
\caption{NOTA: ESTA FIGURA TIENE QUE ACTUALIZARSE CON LA ADAPTATIVA!!!!! Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands.}
  \label{fig:adaptive}
\end{figure*}
% --------------------------------------------------------------

>>>>

\usepackage{moreverb,url,color}

@@

The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey}. These kind of problems require a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration. Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality. In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately. One example of application of this technique was described in \citep{Kimovski15Parallel}. The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes. A high dimensional problem was used to compare these
alternatives. In \citep{Dorronsoro13superlinear}, a distributed coevolutionary island model was used.  Although in both previous works significant speedups were attained, only a low number of nodes were used (8). However, when increasing the number of islands, the division of each section of the chromosome becomes smaller, and the scalability may be affected by obtaining lower quality solutions in the same amount of time.

@@

The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
the compared algorithms and the used methodology (Section 3) are presented. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/
Then, the results of the experiments are shown (Section 4), followed by conclusions and suggestions for future work lines.

@@

These metrics have been used extensively, especially in some of the papers presented previously in Section 2.

@@

This algorithm is a regular NSGA-II algorithm distributed along a number $P$ of islands. After a fixed number of generations, one individual is migrated to another random island. At the end of the run, all PFs of all islands are aggregated in a new one to compute the quality measures. This method as been chosen as it do not require synchronization of the global PF every certain number of generations, as other methods described in Section 2, and because it can {\color{red} QUE MAS SE PUEDE PONER AQUI PARA JUSTIFICARLO?}
%% some justification on why this was chosen - JJ PABLO: Added 
%
%% And some liaison to next subsection - JJ
This method will be compared to different coevolutionary approaches, that are similar to the baseline, with the exception on the decision space to explore in each island.
\subsection{Coevolutionary algorithms compared}
Three different coevolutionary methods have also been used. In all these methods, each island only performs crossover and mutation in specific sections of the individuals.

@@

\begin{figure*}
\centering
\includegraphics[width=12cm]{islandNoDisjoint.jpg}
\caption{{\color{red} NOTA: ESTA FIGURA TIENE QUE ACTUALIZARSE CON LA ADAPTATIVA!!!!!} Adaptive overlapping algorithm: every island $p$ modifies the  $p+c$,
  $p_{th}$ and $p-c$  components (in grey) of the individuals. $c$ is calculated depending on the number of islands.}
  \label{fig:adaptive}
\end{figure*}
% --------------------------------------------------------------
